---
title: "In Class Lab - DIY Functions"
author: "Dr. Shoemaker"
date: "DATA 2401"
output: html_document
---
**Note: Your exam will be in a similar format to this (RMarkdown File with Questions and Code chunks for your answers), so make sure you have the process for knitting to html working.** 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In Class Activity 
The questions from your notes today are below, please copy your answers them here! Then complete the two new tasks, and attempt the "hard mode" if you have time. 

1. Write your own function that takes the temperature in Fahrenheit as an argument and returns the Celcius equivalent. 

```{R -temp converter}
temp_convert <- function(fahrenheit) {
  celcius <- (fahrenheit-32)*(5/9)
  celcius
}

temp_convert(32)

```

2. Expand that function so that it takes a temperature in Fahrenheit and a distance in feet and returns **both** the temperature in Celcius and the distance in meters (you'll likely need to remember the `c()` function!)


```{r -Temperature and feet}
temp_feet_convert <- function(fahrenheit, feet) {
  celcius <- (fahrenheit-32)*(5/9)
  celcius
  
  meters <- feet * .3048
  
  c(celcius, meters)
}

temp_feet_convert(32, 12)
```


3. Write a function that prints out a statement of whether the number passed as an argument is positive, negative or 0. 

```{R -Number sorter}
pos_or_neg <- function(number) {
  # ifs
  if (is.character(number)) {
    statement <- "Please pass a numerical value to this function"
  }
    else if (is.numeric(number)) {
   if(number > 0) {
    statement <- "positive"
  }
    else if (number < 0) {
    statement <- "negative"
  } 
    else if (number == 0) {
    statement <- "zero"
    }
  else  {
    statement <- "Hello World"
  }
  }
    statement
}
# test results

pos_or_neg(12)
pos_or_neg(-2)
pos_or_neg(0)
pos_or_neg("string")
```

4. Write a function that returns the absolute value of the number passed as an argument.
   + Don't use `abs()`. Use the flow from problem 1 and multiply by negative one as necessary. 
   
```{r -absolute value hard way}
abs_value <- function(number) {
  
   if (is.character(number)) {
    absvalue <- "Please pass a numerical value to this function"
  }
  else if (is.numeric(number)) {
     if (number >= 0) {
    absvalue <- number
    }
    else if (number < 0) {
      absvalue <- number * -1
    }
  }
  absvalue
}

abs_value(-124)
abs_value(0)
abs_value(424013551)
abs_value("string")

```

5. Hard mode: add an error check to that function that prints out the string "Please pass a numerical value to this function" if the user passes the function a string. 
   + There are functions that check and return T/F: `is.numeric()` or `is.character()` would be relevant here
   
```{r - Hard Mode??}
hard_mode <- function(check) {
  if (is.character(check)) {
    statement <- "Please pass a numerical value to this function"
  }
    else if (is.numeric(check)) {
      statement <- "good job buddy"
    }
  statement
}
  
hard_mode("same time tomorrow?")
hard_mode(315)

```
   
   






```

